\subsection{Ideal Dilute Solution and Ideal Gasses}
The mass transfer equations in MSR xenon analysis, discussed in section \ref{sec:MT_Phases}, use the ideal gas law, $p=CRT$, and Henry's law, $C=Hp$, in their formulation.  The application of Henry's law assumes an \textit{ideal dilute solution} of xenon in molten-salt wherein the concentration of xenon in molten salt approaches zero.  As the xenon/salt solution deviates from an ideal dilute solution, so to does its adherence to Henry's law.  Furthermore, the application of the ideal gas law assumes the gas pressure is sufficiently low that collisions of gas molecules are negligible.

A number of non-ideal gas laws exist such as the van der Waals equation or Virial equation of state.  A measure of the ideality of a gas can be found using the compressibility factor, $Z=pV /nRT $, which for ideal gasses is defined as 1. NIST REFPROP contains compressibiltiy factor data for many substances. \cite{Lemmon2002} No analyses were found that accounted for non-ideal gas behavior.


In consieration of thee ideal dillute solution assumption, we observe the following: Fletcher reports a macroscopic discrete phase inclusion will form if the radius exceeds the a embryo of dispersed phase atoms exceeds the critical radius,
\begin{equation}
    r_c = \frac{2\sigma}{\Delta G_V}.
\end{equation}\cite{Fletcher1958}
Westh and Haynes investigated the bounds of the domain of concentrations where Henry's Law is applicable,  the Henry region, in water and hexane using a number of solutes. \cite{Westh1998} Westh and Haynes were unable to determine the Henry region due to the limits of the calorimeter used; however, they were able to give a lower limit for non-Henry behavior on the order of $10^{-4}$, for hexane solvents and solutes, and $10^{-5}$, for a water solute and a number of solvents.   As previously mentioned, Grimes, Blander and Watson established solubility limits for xenon in molten salts, above which no further xenon could dissolve in their experimental apparatus. \cite{Grimes1958,Blander1959,Watson1962}
\input{GFX/img_concMap.tex}
Given these observations, we posit the following: Consider figure \ref{concMap}.  This figure represents the phase space of xenon and other-gas concentrations within the molten salt system.  There is then, three regions, H,N,and B.  The Henry region, H, is where Henry's law is applicable; The Non-Henery region, N is where Henry's law is not applicable, but the salt melt has yet to reach gas saturation; finally, B, the bubble-out region, is where the salt melt has reached saturation and additional gas evolution forms dispersed gas-phase inclusions rather than dissolving into the salt melt.  No evidence has been found that indicates the H/N boundary exhibits any sort of sharp discontinuous behavior, and we suspect the transition from Henry-like to non-Henry-like behavior exhibits a \textit{smooth} character.  One potential criterion for the H/N boundary is the xenon concentration such that the ratio of the xenon to partial pressure is greater than multiple, K, of the Henry constant,
\begin{equation}
    C_i^L \; S.T. \; \frac{C_i^L}{p_i^g} > KH_i.
\end{equation}
Since the Henry constant is a function of temperature, pressure, and composition, it likewise follows the location of the  H/N boundary is a function of temperature, pressure, and composition. 
Consider a volume of salt melt with xenon and other gasses dissolved in it. This salt melt also contains actinides that are udergoing fission.  As the actinides undergo fission, a fraction of their fission products are gaseous.  If we track the behavior of these gaseous fission products, including xenon, then there is a certain probability per unit time that the gaseous products will join a gas embryo of radius greater than the critical radius.  This probability is a function of the quantity of gas within the salt melt.  We posit the N/B boundary is the total gas concentration such that a gas atom is more likely than not to join a gas embryo of radius greater than critical radius.  Since the critical radius is a function of the surface tension and Gibbs free energy, and these are functions of temperature and composition, and for the case of the Gibbs free energy, the pressure, the N/B boundary is likewise a function of temperature, pressure and composition.

All the xenon modeling efforts to date have focused on modeling efforts within the H region.  No work was found that did not use Henry's law the formulation of the mass transfer equations.